Supplementary Material \--- Laves polyhedrons in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and the lattice dynamics

### 2021-01-16 SM/paper_tennantite.tex
Interatomic distances and Summary of crystallographic information tables changed

\begin{table}
\caption{\label{tab:inter_dist}
Interatomic distances in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lccc}
Distance&
Averaged, \AA  &
Extinct, \AA  &
Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
Cu1 -- S1$\times$4   & 2.3177(17) & 2.315511)  & 2.3099(6) \\
Cu2 -- Cu21$\times$2 & 0.92(2)    & 0.891(11)  & 0.95(3) \\
Cu2 -- S1$\times$2   & 2.215(4)   & 2.211(3)   & 2.219(3) \\
Cu2 -- S2            & 2.212(7)   & 2.224(4)   & 2.206(5) \\
Cu21 -- S1$\times$2  & 2.421(18)  & 2.427(11)  & 2.427(17) \\
Cu21 -- S2           & 2.356(15)  & 2.326(11)  & 2.380(14) \\
As1 -- S1$\times$3   & 2.2505(18) & 2.2503(12) & 2.2457(19) \\
Cu21 -- As1          & 2.58(2)    & 2.604(11)  & 2.535(19) \\
Cu2 -- As1           & 3.4832(11) & 3.4816(7)  & 3.480(4) \\

@@

a, \AA                                                     & \multicolumn{2}{c}{10.1742(2)}	                              	             & 10.1572(2)	\\
V, \AA\textsuperscript{3}                                  & \multicolumn{2}{c}{1053.19(4)}	                              	             & 1047.91(4)	\\
S.G.                                                       & \multicolumn{3}{c}{1053.19(4)}	                                             	\\
Radiation, wavelength (\AA)                                & \multicolumn{2}{c}{Ag K\textsubscript{$\alpha$}, 0.56089}		                        	             & Mo K\textsubscript{$\alpha$}, 0.71069	\\
Diffractometer                                             & \multicolumn{2}{c}{CAD4}	                                                  & Xcalibur	\\
Absorption correction                                      & \multicolumn{2}{c}{Analytical (sphere)}	                    	             & Analytical (crystal shape)	\\
q\textsubscript{max}, deg.                                 & \multicolumn{2}{c}{29.85}	                                  	             & 42.08	\\
R\textsubscript{int}                                       & 0.041	                                                     & ---	         & 0.049	\\
N\textsubscript{ref} , collected                           & \multicolumn{2}{c}{3509}	                                    	             & 11026	\\
N\textsubscript{ref} , independent, $I\geqslant2\sigma(I)$ & 553	                                                       & 2840	         & 667	\\
N\textsubscript{paf}                                       & 50	                                                         & 55	           & 44	\\
Refinement on                                              & \multicolumn{2}{c}{$|F|^2$}	                                	             & $|F|$	\\
Anharmonic, Atoms (rank)                                   & \multicolumn{2}{c}{Cu1(4), Cu2(3), Cu21(3), S1(3), As1(3)}	  	             & Cu1(4), Cu2(3), Cu21(3), S2(4)	\\
GOF                                                        & 1.01	                                                       & 1.04	         & 1.00	\\
R/{\it w}R\textsubscript{2}                                & 0.025/0.066	                                               & 0.038/0.098	 & 0.029/0.038	\\
Min. Negative JPDF, \% of positive                         & -2.7	                                                       & 	             & -3.4	\\
$\pm\Delta\rho$, {\it e}\AA\textsuperscript{-3}            & +0.7/–0.63	                                                 & +0.95/–1.32	 & +1.7/–1.2	\\

>>>>

\begin{table}
\caption{\label{tab:inter_dist}
Interatomic distances in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lccc}
Distance&
Averaged, \AA  &
Extinct, \AA  &
Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
Cu1 -- S1$\times$4   & 2.3177(17) & 2.3147(10) & 2.3099(6) \\
Cu2 -- Cu21$\times$2 & 0.890(17)  & 0.868(9)   & 0.95(3) \\
Cu2 -- S1$\times$2   & 2.208(4)   & 2.211(3)   & 2.219(3) \\
Cu2 -- S2            & 2.219(6)   & 2.223(4)   & 2.206(5) \\
Cu21 -- S1$\times$2  & 2.421(18)  & 2.420(10)  & 2.427(17) \\
Cu21 -- S2           & 2.326(15)  & 2.316(10)  & 2.380(14) \\
As1 -- S1$\times$3   & 2.2543(19) & 2.2530(10) & 2.2457(19) \\
Cu21 -- As1          & 2.604(17)  & 2.626(10)  & 2.535(19) \\
Cu2 -- As1           & 3.4816(11) & 3.4813(7)  & 3.480(4) \\

@@

a, \AA                                                     & \multicolumn{2}{c}{10.1742(2)}	                              	             & 10.1572(2)	\\
V, \AA\textsuperscript{3}                                  & \multicolumn{2}{c}{1053.19(4)}	                              	             & 1047.91(4)	\\
S.G.                                                       & \multicolumn{3}{c}{ \hmn{I -4 3 m} }	                                             	\\
Radiation, wavelength (\AA)                                & \multicolumn{2}{c}{Ag K\textsubscript{$\alpha$}, 0.56089}		                & Mo K\textsubscript{$\alpha$}, 0.71069	\\
Diffractometer                                             & \multicolumn{2}{c}{CAD4}	                                                  & Xcalibur	\\
Absorption correction                                      & \multicolumn{2}{c}{Analytical (sphere)}	                    	             & Analytical (crystal shape)	\\
$\Theta$\textsubscript{max}, deg.                                 & \multicolumn{2}{c}{29.85}	                                  	             & 42.08	\\
R\textsubscript{int}                                       & 0.046	                                                     & ---	         & 0.049	\\
N\textsubscript{ref} , collected                           & \multicolumn{2}{c}{3509}	                                    	             & 11026	\\
N\textsubscript{ref} , independent, $I\geqslant2\sigma(I)$ & 570	                                                       & 2837	         & 667	\\
N\textsubscript{paf}                                       & 50	                                                         & 55	           & 44	\\
Refinement on                                              & \multicolumn{2}{c}{$|F|$}	                                	             & $|F|$	\\
Anharmonic, Atoms (rank)                                   & \multicolumn{2}{c}{Cu1(4), Cu2(3), Cu21(3), S1(3), As1(3)}	  	             & Cu1(4), Cu2(3), Cu21(3), S2(4)	\\
GOF                                                        & 1.01	                                                       & 1.04	         & 1.00	\\
R/{\it w}R\textsubscript{2}                                & 0.028/0.036	                                               & 0.038/0.050	 & 0.029/0.038	\\
Min. Negative JPDF, \% of positive                         & -2.7	                                                       & 	-3.8             & -3.4	\\
$\pm\Delta\rho$, {\it e}\AA\textsuperscript{-3}            & +0.64/–0.76	                                                 & +1.18/–0.61	 & +1.7/–1.2	\\
